% --------------------------
% Arnold Gnanaselvam — Resume (Targeting Microsoft Software Engineer II - Azure/Cloud)
% Highlights: Java, C# ability, Distributed Systems, Reliability
% --------------------------
\documentclass[11pt]{article}
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{fontspec}
\setmainfont{Arial}
\titleformat{\section}{\large\bfseries}{}{0em}{}\renewcommand{\familydefault}{\sfdefault}

\begin{document}
% Header
{\LARGE \textbf{Arnold Gnanaselvam}}\\
Cuddalore, Tamil Nadu, India \quad | \quad +91 9361097319 \quad | \quad \href{mailto:arnoldgna765@gmail.com}{arnoldgna765@gmail.com}\\
\href{https://github.com/arnold-1324}{github.com/arnold-1324} \quad | \quad \href{https://leetcode.com/u/arnold/}{leetcode.com/u/arnold/}

\vspace{6pt}
\hrule
\vspace{6pt}

\section*{Summary}
Backend software engineer specializing in **Distributed Systems** and **Cloud Services**. Experienced in building scalable ($<$100ms latency) microservices and reliable ingestion pipelines. Strong foundation in object-oriented design (Java) with readiness to adapt to C#/.NET environments. Skilled in ensuring system reliability through observability, SLO definition, and chaos engineering testing.

\section*{Experience}
\textbf{Synthesis Healthsoft Service \& Solutions LLP} \hfill June 2024 -- Present\\
\textit{Junior Software Developer} \hfill Chennai, India
\begin{itemize}[leftmargin=*]
  \item \textbf{Scalable Microservices}: Designed and deployed a high-performance indexing service handling 60K daily requests with sub-100ms latency.
  \item \textbf{Reliability Engineering}: Implemented CI/CD performance gates and comprehensive monitoring to protect service SLAs; led post-incident reviews to drive structural fixes.
  \item \textbf{Data Consistency}: Built an event-driven ingestion pipeline ensuring data durability and correctness through batching and backpressure mechanisms.
  \item \textbf{Engineering Rigor}: Reduced production incidents by enforcing strict code review checklists (tests, docs, metrics) and mentoring peers on quality standards.
\end{itemize}

\section*{Technical Projects}
\textbf{Distributed Caching System} \hfill \textit{Java, TCP/IP, P2P}
\begin{itemize}[leftmargin=*]
  \item Developed a peer-to-peer cache demonstrating **eventual consistency** and replication strategies relevant to large-scale cloud storage.
  \item Tested system resilience against network partitions (Split-brain) and node failures, ensuring high availability.
\end{itemize}

\textbf{Resilient Ingestion Pipeline} \hfill \textit{Node.js, Redis, Elasticsearch}
\begin{itemize}[leftmargin=*]
  \item Architected a fault-tolerant ingestion system capable of graceful recovery and event replay under load.
  \item Integrated automated performance tests into the build pipeline to detect latency regressions early.
\end{itemize}

\section*{Technical Skills}
\begin{tabular}{p{0.3\linewidth} p{0.65\linewidth}}
\textbf{Languages:} & Java, Python, JavaScript/TypeScript (Open to C#/.NET) \\
\textbf{Backend & Systems:} & Microservices, Distributed Caching, Event-Driven Architecture \\
\textbf{Database:} & SQL (PostgreSQL), NoSQL (Redis, Elasticsearch) \\
\textbf{Cloud & Ops:} & AWS, Azure concepts, Docker, Kubernetes, CI/CD \\
\textbf{Quality:} & Unit/Integration Testing, SLOs/SLIs, Incident Management \\
\end{tabular}

\section*{Education}
\textbf{B.Sc. Computer Science} \hfill Bishop Heber College (2021--2024)

\section*{Continuous Learning}
Actively learning **Go** and studying **Distributed Consensus** (Paxos/Raft) to deepen understanding of cloud-native infrastructure.

\end{document}
